Manuscript 1 code

### 2024-10-10 manuscript_1_code.Rmd
commented out unwanted code
fixed ranges on figure 5

dss_spatial_ranges <- dss_spatial_2 %>%
  group_by(habitat) %>%
  summarise(min_spatial_synchrony = min(dss_spatial_2$spatial_synchrony, na.rm = TRUE),
            max_spatial_synchrony = max(dss_spatial_2$spatial_synchrony, na.rm = TRUE),
            min_mean_synchrony= min(synchrony_mean, na.rm = TRUE),
            max_mean_synchrony = max(synchrony_mean, na.rm  = TRUE))

@@

## models
```{r model spatial synchrony}
spatial_synchrony_mod <- glmmTMB(cover_stability ~ spatial_synchrony*habitat, family = Gamma("log"), data = dss_spatial_2)
hist(residuals(spatial_synchrony_mod)) # a little skew
plot(residuals(spatial_synchrony_mod) ~ predict(spatial_synchrony_mod))
summary(spatial_synchrony_mod)
Anova(spatial_synchrony_mod)
#                             Chisq Df Pr(>Chisq)    
# spatial_synchrony         16.2914  1  5.431e-05 ***
# habitat                   19.5303  3  0.0002124 ***
# spatial_synchrony:habitat  6.7239  3  0.0812368 .  
emtrends(spatial_synchrony_mod, pairwise ~ habitat, var = "spatial_synchrony") # no sig differences but close
# contrast                    estimate    SE  df z.ratio p.value
# Fringing - Backreef            0.404 1.765 Inf   0.229  0.9958
# Fringing - Forereef 10m        1.365 1.754 Inf   0.778  0.8643
# Fringing - Forereef 17m        3.112 1.882 Inf   1.654  0.3484
# Backreef - Forereef 10m        0.961 0.857 Inf   1.121  0.6766
# Backreef - Forereef 17m        2.708 1.095 Inf   2.472  0.0644
# Forereef 10m - Forereef 17m    1.747 1.078 Inf   1.621  0.3668
```
```{r plot spatial synchrony}
spat_stab_emm <- emmip(spatial_synchrony_mod,
                        habitat ~ spatial_synchrony,
                        at = list(spatial_synchrony = seq(0,1,0.01)), plotit = F, CIs = T)

@@

```
```{r mean synchrony}
mean_synchrony_mod <- glmmTMB(cover_stability ~ synchrony_mean*habitat, family = Gamma("log"), data = dss_spatial_2)
hist(residuals(mean_synchrony_mod)) # chunky
plot(residuals(mean_synchrony_mod) ~ predict(mean_synchrony_mod)) # heteroskedastic
summary(mean_synchrony_mod)
Anova(mean_synchrony_mod)
#                         Chisq Df Pr(>Chisq)    
# synchrony_mean         30.134  1  4.031e-08 ***
# habitat                22.008  3  6.498e-05 ***
# synchrony_mean:habitat 17.251  3  0.0006275 ***
emtrends(mean_synchrony_mod, pairwise ~ habitat, var = "synchrony_mean") # no sig differences but close
# contrast                    estimate   SE  df z.ratio p.value
# Fringing - Backreef            -2.75 1.79 Inf  -1.538  0.4147
# Fringing - Forereef 10m         2.57 1.05 Inf   2.444  0.0691
# Fringing - Forereef 17m         3.73 1.27 Inf   2.946  0.0170
# Backreef - Forereef 10m         5.33 1.85 Inf   2.875  0.0211
# Backreef - Forereef 17m         6.48 1.98 Inf   3.271  0.0059
# Forereef 10m - Forereef 17m     1.15 1.35 Inf   0.853  0.8287
```
```{r plot mean synchrony}
mean_synch_emm <- emmip(mean_synchrony_mod,
                        habitat ~ synchrony_mean,
                        at = list(synchrony_mean = seq(0,1,0.01)), plotit = F, CIs = T)

@@

ggsave(filename = "output/figure_5.png", figure_5, height = 8, width = 16)
```

>>>>

dss_spatial_ranges <- dss_spatial_2 %>%
  group_by(habitat) %>%
  summarise(min_spatial_synchrony = min(spatial_synchrony, na.rm = TRUE),
            max_spatial_synchrony = max(spatial_synchrony, na.rm = TRUE),
            min_mean_synchrony= min(synchrony_mean, na.rm = TRUE),
            max_mean_synchrony = max(synchrony_mean, na.rm  = TRUE))

@@

## models
```{r model spatial synchrony}
spatial_synchrony_mod <- glmmTMB(cover_stability ~ spatial_synchrony*habitat, family = Gamma("log"), data = dss_spatial_2)
hist(residuals(spatial_synchrony_mod)) # a little skew
plot(residuals(spatial_synchrony_mod) ~ predict(spatial_synchrony_mod))
summary(spatial_synchrony_mod)
Anova(spatial_synchrony_mod)
#                             Chisq Df Pr(>Chisq)    
# spatial_synchrony         16.2914  1  5.431e-05 ***
# habitat                   19.5303  3  0.0002124 ***
# spatial_synchrony:habitat  6.7239  3  0.0812368 .  
emtrends(spatial_synchrony_mod, pairwise ~ habitat, var = "spatial_synchrony") # no sig differences but close
# contrast                    estimate    SE  df z.ratio p.value
# Fringing - Backreef            0.404 1.765 Inf   0.229  0.9958
# Fringing - Forereef 10m        1.365 1.754 Inf   0.778  0.8643
# Fringing - Forereef 17m        3.112 1.882 Inf   1.654  0.3484
# Backreef - Forereef 10m        0.961 0.857 Inf   1.121  0.6766
# Backreef - Forereef 17m        2.708 1.095 Inf   2.472  0.0644
# Forereef 10m - Forereef 17m    1.747 1.078 Inf   1.621  0.3668
```

```{r plot spatial synchrony}
spat_stab_emm <- emmip(spatial_synchrony_mod,
                        habitat ~ spatial_synchrony,
                        at = list(spatial_synchrony = seq(0,1,0.01)), plotit = F, CIs = T)

@@

```{r mean synchrony}
mean_synchrony_mod <- glmmTMB(cover_stability ~ synchrony_mean*habitat, family = Gamma("log"), data = dss_spatial_2)
hist(residuals(mean_synchrony_mod)) # chunky
plot(residuals(mean_synchrony_mod) ~ predict(mean_synchrony_mod)) # heteroskedastic
summary(mean_synchrony_mod)
Anova(mean_synchrony_mod)
#                         Chisq Df Pr(>Chisq)    
# synchrony_mean         30.134  1  4.031e-08 ***
# habitat                22.008  3  6.498e-05 ***
# synchrony_mean:habitat 17.251  3  0.0006275 ***
emtrends(mean_synchrony_mod, pairwise ~ habitat, var = "synchrony_mean") # no sig differences but close
# contrast                    estimate   SE  df z.ratio p.value
# Fringing - Backreef            -2.75 1.79 Inf  -1.538  0.4147
# Fringing - Forereef 10m         2.57 1.05 Inf   2.444  0.0691
# Fringing - Forereef 17m         3.73 1.27 Inf   2.946  0.0170
# Backreef - Forereef 10m         5.33 1.85 Inf   2.875  0.0211
# Backreef - Forereef 17m         6.48 1.98 Inf   3.271  0.0059
# Forereef 10m - Forereef 17m     1.15 1.35 Inf   0.853  0.8287
```
```{r plot mean synchrony}
mean_synch_emm <- emmip(mean_synchrony_mod,
                        habitat ~ synchrony_mean,
                        at = list(synchrony_mean = seq(0,1,0.01)), plotit = F, CIs = T)

@@

# ggsave(filename = "output/figure_5.png", figure_5, height = 8, width = 16)
```
